Exploratory Plots

### 2020-10-16 exploratory/2020/sub3_fit_all-seqs.Rmd

```{r mem}
dat %>% group_by(num_ref_seqs, dataset, ref_weight, method) %>% 
  summarize(mean_mem_gb=mean(mem_gb)) %>% 
  ggplot(aes(x=num_ref_seqs, y=mean_mem_gb, color=dataset)) +
  geom_point(alpha = 0.5) +
  geom_point(aes(x=num_ref_seqs, y=mean_mem_gb), denovo_sum, shape='triangle') +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  scale_x_continuous(breaks = seq(0, 300000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k', '250k', '300k')) +
  labs(title = 'Memory usage over reference size',
       x = '# sequences in reference',
       y = 'MB',
       caption = 'Triangles: mean runtime for _de novo_ clustering on the entire dataset') +
  theme(plot.caption = element_markdown())
dat %>% group_by(num_ref_seqs, dataset, ref_weight, method) %>% 
  summarize(mean_mem_gb=mean(mem_gb)) %>% 
  ggplot(aes(x=num_ref_seqs, y=mean_mem_gb, color=ref_weight)) +
  geom_point(alpha = 0.5) +
  geom_point(aes(x=num_ref_seqs, y=mean_mem_gb, color=NULL), denovo_sum, shape='triangle') +
  facet_grid(dataset ~ method, scales = 'free') +
  scale_x_continuous(breaks = seq(0, 300000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k', '250k', '300k')) +
  labs(title = 'Memory usage over reference size',
       x = '# sequences in reference',
       y = 'MB',
       caption = 'Black triangles: mean runtime for _de novo_ clustering on the entire dataset') +
  theme(plot.caption = element_markdown())
```

>>>>

```{r mem}
dat %>% group_by(num_ref_seqs, dataset, ref_weight, method) %>% 
  summarize(mean_mem_gb=mean(mem_gb)) %>% 
  ggplot(aes(x=num_ref_seqs, y=mean_mem_gb, color=dataset)) +
  geom_point(alpha = 0.5) +
  geom_point(aes(x=num_ref_seqs, y=mean_mem_gb), denovo_sum, shape='triangle') +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  scale_x_continuous(breaks = seq(0, 300000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k', '250k', '300k')) +
  labs(title = 'Memory usage over reference size',
       x = '# sequences in reference',
       y = 'GB',
       caption = 'Triangles: mean runtime for _de novo_ clustering on the entire dataset') +
  theme(plot.caption = element_markdown())
dat %>% group_by(num_ref_seqs, dataset, ref_weight, method) %>% 
  summarize(mean_mem_gb=mean(mem_gb)) %>% 
  ggplot(aes(x=num_ref_seqs, y=mean_mem_gb, color=ref_weight)) +
  geom_point(alpha = 0.5) +
  geom_point(aes(x=num_ref_seqs, y=mean_mem_gb, color=NULL), denovo_sum, shape='triangle') +
  facet_grid(dataset ~ method, scales = 'free') +
  scale_x_continuous(breaks = seq(0, 300000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k', '250k', '300k')) +
  labs(title = 'Memory usage over reference size',
       x = '# sequences in reference',
       y = 'GB',
       caption = 'Black triangles: mean runtime for _de novo_ clustering on the entire dataset') +
  theme(plot.caption = element_markdown())
```
